Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-09-14 paper/paper.tex
Monday's WIP

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_wt.png}
\caption{Gradient following model with axon-axon interactions.}
\label{f:wt}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GC_wt_rotcmp.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GC_tecrot90.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GC_tecrot180.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GC_tecswap.png}
\end{subfigure}
\caption{Surgical manipulations. Row A: wildtype. Row B: 90 degree
rotation. Row C: 180 degree rotation. Row D: Graft swap.}
\label{f:surg1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_manipulations2.png}
\caption{Surgical manipulations 2. Row A: Retinal ablation, Row B: Tectal
ablation, Row C: Mismatch (ablate retina and also the tectum that matches the
left-behind retina), Row D: Compound eye (Two nasal retinal halves `glued
together')}
\label{f:surg2}
\end{figure}

>>>>

The I interaction is absent when the topographic ordering is good. This means
that it does not fix the retablate condition. Like the other competition
effects, it is strongly affected by the radius of interaction.

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_wt_fig.png}
\caption{Gradient following model with axon-axon interactions.}
\label{f:wt}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_wt_rotcmp.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_tecrot90.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_tecrot180.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_tecswap.png}
\end{subfigure}
\caption{Surgical manipulations. Row A: wildtype. Row B: 90 degree
rotation. Row C: 180 degree rotation. Row D: Graft swap.}
\label{f:surg1}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_retablate.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_tecablate.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_mismatch.png}
\end{subfigure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\linewidth]{./images/j4_eE_GJ_compound.png}
\end{subfigure}
\caption{Surgical manipulations 2. Row A: Retinal ablation, Row B: Tectal
ablation, Row C: Mismatch (ablate retina and also the tectum that matches the
left-behind retina), Row D: Compound eye (Two nasal retinal halves `glued
together')}
\label{f:surg2}
\end{figure}
